An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-28 article.tex
Minor edits

\begin{document}
\begin{linenumbers}
\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

    \title{An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

    \affiliation[label1]{organization={QUT},
                 addressline={},
                 city={},
                 postcode={},
                 state={QLD},
                 country={}}
    \affiliation[label2]{organization={AWRI},
                 addressline={},
                 city={},
                 postcode={},
                 state={SA},
                 country={}}
    \affiliation[label3]{organization={Food Agility CRC},
                 addressline={},
                 city={},
                 postcode={},
                 state={Vic},
                 country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}

    \begin{abstract}
      %% Text of abstract
      Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
      \end{abstract}

      %%Graphical abstract
      \begin{graphicalabstract}
        \includegraphics{graphical_abstract.jpeg}
      \end{graphicalabstract}

      \begin{keyword}
      %% keywords here, in the form: keyword \sep keyword
      Keyword one \sep{} keyword two
      %% PACS codes here, in the form: \PACS code \sep code
      \PACS{} 0000 \sep{} 1111
      %% MSC codes here, in the form: \MSC code \sep code
      %% or \MSC[2008] code \sep code (2000 is the default)
      \MSC{} 0000 \sep{} 1111
      \end{keyword}

      %%Research highlights
      \begin{highlights}
        \item Research highlight 1
        \item Research highlight 2
        \end{highlights}

      \end{frontmatter}

@@

\subsection{Exploratory Analysis} \label{sec:exp_anal}

@@

To determine if a coefficient was indicative of a strong relationship, confidence intervals were used. P-values reflected the significance of a given correlation coefficient when considering its relation to sample size via its incorporation as an element of standard error. Strong relationships were found to be present as all P-values, except for the non-transformed values for water used, were considered significant (P \< 2.200E-16).

@@

The coefficients of each model describe the relationship of a predictor variable to its response when considering all other predictor variables. Due to the transformations of the data, coefficients are individually interpreted in the same manner as the prior regression values were (see section\ref{sec:exp_anal}); although all coefficients need to be considered together. Unlike the regression values the coefficients range is not limited between -1 and 1, as each variable's contribution needs to be considered together.

@@

We look at the coefficients of categorical and continuous variables  separately. This is primarily done as the categorical variables have many coefficients, one for each category, whilst continuous variables have only one. The coefficient for categorical variables is summarised in Figure\ref{fig:violin}; illustrating the difference in the range and the affect region and year could have on each of the models. Comparatively, the continuous variables coefficients are summarised in Table\ref{tab:contvar}.
In terms of magnitude, GI region has the highest possible absolute value for each model. An important consideration is that region and year are binary variables, such that they are only equal to zero or the coefficient (as they will present as a value of 1 multiplied by the coefficient); this means that, although region may have a strong relationship, it can be overshadowed by an extreme value of one of the continuous variables. The most notable difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested has the opposite sign between them. These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 

@@

\subsubsection{Model Comparisons: Productivity Verse Value}
% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.

%
%Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.

(see Table \ref*{tab:modelperformance}). 
% This is important but you do not illustrate why
%
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
%% Text of abstract
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC{} 0000 \sep{} 1111
\end{keyword}
%%Research highlights
\begin{highlights}
  \item Research highlight 1
  \item Research highlight 2
\end{highlights}
\end{frontmatter}

@@

\subsection{Exploratory Analysis}\label{sec:exp_anal}

@@

To determine if a coefficient was indicative of a strong relationship, confidence intervals were used. P-values reflected the significance of a given correlation coefficient when considering its relation to sample size via its incorporation as an element of standard error. Strong relationships were found to be present as all P-values, except for the non-transformed values for water used, were considered significant (P $<$ 2.200E-16).

@@

The coefficients of each model describe the relationship of a predictor variable to its response when considering all other variables. Due to the transformations of the data, coefficients are individually interpreted in the same manner as the prior regression values were (see Section \ref{sec:exp_anal}); unlike the regression values,  coefficient ranges are not limited between -1 and 1, as each variable needs to be considered together.

@@

We look at the coefficients of categorical and continuous variables separately. This is primarily done as the categorical variables have many coefficients, one for each category, whilst continuous variables have only one. The coefficient for categorical variables is summarised in Figure\ref{fig:violin}; illustrating the difference in the range as well as affect region and year could have on each of the models. Comparatively, the continuous variables coefficients are summarised in Table \ref{tab:contvar}.
In terms of magnitude, GI region has the highest possible absolute value for each model. An important consideration is that region and year are binary, such that they are only equal to zero or the coefficient (as they will present as a value of 1 which will be multiplied by the coefficient); this means that, although region may have a strong relationship, it can be overshadowed by an extreme value of one of the continuous variables. The most notable difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested had the opposite sign. These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 

@@

\subsubsection{Model Comparisons: Yield Verse Value}

% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
%
%Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.
%(see Table \ref*{tab:modelperformance}). 
% This is important but you do not illustrate why
%
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.
